---
title: "Market Segmentation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Market Segmentation}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

This document will guide readers through how to reproduce the results
presented in the article [Interactively Visualizing Multivariate Market
Segmentation Using the R Package
Lionfish](https://github.com/mmedl94/lionfish_article) submitted to the
[Austrian Journal of Statistics](https://www.ajs.or.at/index.php/ajs).

## General note

All scripts are designed to be run from top to bottom. If you only want to run parts of the scripts you will have to make sure that init_inv() is run before using any lionfish function!

## Preparation

In order to run reproduce all results you will have to

1.  install lionfish,

2.  install the development version of tourr,

3.  and download and unzip the repository.

### Installation of lionfish

lionfish is now available on CRAN!

```{r, eval = FALSE}
install.packages("lionfish")
```

You can install the development version of lionfish from github with:

```{r, eval = FALSE}
install.packages("remotes")
remotes::install_github("mmedl94/lionfish")
```

Make sure you have git installed. You can download and install git from
<https://git-scm.com/downloads>.

Complications may arise when installing and accessing the Python backend
of this package. If you run into any, please don't refrain from opening
an issue!

### Download github repository

You can download the repository either as .zip by clicking the green
button that says "Code" on the top right and then click "Download ZIP".
This will be necessary to load the lionfish snapshots.

```{r load packages}
library(lionfish)
library(data.table)
library(tourr)
if (requireNamespace("tidyverse")) {library(tidyverse)}
if (requireNamespace("mvtnorm")) {library(mvtnorm)}
if (requireNamespace("patchwork")) {library(patchwork)}
if (requireNamespace("colorspace")) {library(colorspace)}
if (requireNamespace("ggbeeswarm")) {library(ggbeeswarm)}
if (requireNamespace("flexclust")) {library(flexclust)}
if (requireNamespace("gridExtra")) {library(gridExtra)}
if (requireNamespace("stats")) {library(stats)}
if (requireNamespace("dplyr")) {library(dplyr)}
```

## Introduction

Figures 1, 2 and 3 shown in the introduction can be reproduced by
running /scripts/intro.R

```{r intro figure 1}
if (requireNamespace(c("tidyverse",
                      "mvtnorm",
                      "patchwork",
                      "colorspace",
                      "ggbeeswarm",
                      "dplyr",
                      "gridExtra"))){
theme_set(theme_bw(base_size = 14) +
            theme(
              aspect.ratio = 1,
              plot.background = element_rect(fill = 'transparent', colour = NA),
              plot.title.position = "plot",
              plot.title = element_text(size = 24),
              panel.background = element_rect(fill = 'transparent', colour = NA),
              legend.background = element_rect(fill = 'transparent', colour = NA),
              legend.key = element_rect(fill = 'transparent', colour = NA)
            )
)

f_std <- function(x) {(x-min(x))/(max(x)-min(x))}
set.seed(914)
blob1 <- rmvnorm(n=155, mean=c(0,0), 
                 sigma=matrix(c(1, 0, 0, 1), 
                              ncol=2, byrow=TRUE)) |> 
  as_tibble() |>
  mutate_all(f_std)
blob2 <- rmvnorm(n=155, mean=c(0,0), 
                 sigma=matrix(c(1, 0.6, 0.6, 1), 
                              ncol=2, byrow=TRUE)) |> 
  as_tibble() |>
  mutate_all(f_std)
blob3 <- rmvnorm(n=155, mean=c(0,0), 
                 sigma=matrix(c(1, 0.9, 0.9, 1), 
                              ncol=2, byrow=TRUE)) |> 
  as_tibble() |>
  mutate_all(f_std)
b1 <- ggplot(blob1, aes(V1, V2)) + 
  geom_point() +
  theme(axis.text = element_blank(),
        axis.title = element_blank())
b2 <- ggplot(blob2, aes(V1, V2)) + 
  geom_point() +
  theme(axis.text = element_blank(),
        axis.title = element_blank())
b3 <- ggplot(blob3, aes(V1, V2)) + 
  geom_point() +
  theme(axis.text = element_blank(),
        axis.title = element_blank())
b1 + b2 + b3 + plot_layout(ncol=3)
}
```

```{r intro figure 2}
if (requireNamespace(c("tidyverse",
                      "mvtnorm",
                      "patchwork",
                      "colorspace",
                      "ggbeeswarm",
                      "dplyr",
                      "gridExtra"))){
set.seed(855)
b1_km <- kmeans(blob1, 4)
b2_km <- kmeans(blob2, 4)
b3_km <- kmeans(blob3, 4)
blob1_cl <- blob1 |>
  mutate(cl = factor(b1_km$cluster))
blob2_cl <- blob2 |>
  mutate(cl = factor(b2_km$cluster))
blob3_cl <- blob3 |>
  mutate(cl = factor(b3_km$cluster))
b4 <- ggplot(blob1_cl, aes(V1, V2, colour=cl)) + 
  geom_point() +
  scale_color_discrete_divergingx(palette="Zissou 1") +
  annotate("text", x=0.05, y=0.95, label="A", size=8) +
  theme(legend.position = "none", 
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())
b5 <- ggplot(blob2_cl, aes(V1, V2, colour=cl)) + 
  geom_point() +
  scale_color_discrete_divergingx(palette="Zissou 1") +
  annotate("text", x=0.05, y=0.95, label="B", size=8) +
  theme(legend.position = "none", 
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())
b6 <- ggplot(blob3_cl, aes(V1, V2, colour=cl)) + 
  geom_point() +
  scale_color_discrete_divergingx(palette="Zissou 1") +
  annotate("text", x=0.05, y=0.95, label="C", size=8) +
  theme(legend.position = "none", 
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())
b4 + b5 + b6 + plot_layout(ncol=3)

b7 <- ggplot(blob1_cl, aes(V1, fill=cl)) + 
  geom_histogram(breaks = seq(0, 1, 0.1)) +
  scale_fill_discrete_divergingx(palette="Zissou 1") +
  ylim(c(0,37)) +
  annotate("text", x=0.05, y=35, label="A", size=8) +
  theme(legend.position = "none", 
        axis.text = element_blank(),
        axis.title.y = element_blank())
b8 <- ggplot(blob2_cl, aes(V1, fill=cl)) + 
  geom_histogram(breaks = seq(0, 1, 0.1)) +
  scale_fill_discrete_divergingx(palette="Zissou 1") +
  ylim(c(0,37)) +
  annotate("text", x=0.05, y=35, label="B", size=8) +
  theme(legend.position = "none", 
        axis.text = element_blank(),
        axis.title.y = element_blank())
b9 <- ggplot(blob3_cl, aes(V1, fill=cl)) + 
  geom_histogram(breaks = seq(0, 1, 0.1)) +
  scale_fill_discrete_divergingx(palette="Zissou 1") +
  ylim(c(0,37)) +
  annotate("text", x=0.05, y=35, label="C", size=8) +
  theme(legend.position = "none", 
        axis.text = element_blank(),
        axis.title.y = element_blank())
b10 <- ggplot(blob1_cl, aes(V2, fill=cl)) + 
  geom_histogram(breaks = seq(0, 1, 0.1)) +
  scale_fill_discrete_divergingx(palette="Zissou 1") +
  ylim(c(0,37)) +
  annotate("text", x=0.05, y=35, label="D", size=8) +
  theme(legend.position = "none", 
        axis.text = element_blank(),
        axis.title.y = element_blank())
b11 <- ggplot(blob2_cl, aes(V2, fill=cl)) + 
  geom_histogram(breaks = seq(0, 1, 0.1)) +
  scale_fill_discrete_divergingx(palette="Zissou 1") +
  ylim(c(0,37)) +
  annotate("text", x=0.05, y=35, label="E", size=8) +
  theme(legend.position = "none", 
        axis.text = element_blank(),
        axis.title.y = element_blank())
b12 <- ggplot(blob3_cl, aes(V2, fill=cl)) + 
  geom_histogram(breaks = seq(0, 1, 0.1)) +
  scale_fill_discrete_divergingx(palette="Zissou 1") +
  ylim(c(0,37)) +
  annotate("text", x=0.05, y=35, label="F", size=8) +
  theme(legend.position = "none", 
        axis.text = element_blank(),
        axis.title.y = element_blank())
b7 + b8 + b9 + b10 + b11 + b12 + plot_layout(ncol=3)
}
```

```{r intro figure 3}
if (requireNamespace(c("tidyverse",
                      "mvtnorm",
                      "patchwork",
                      "colorspace",
                      "ggbeeswarm",
                      "dplyr",
                      "gridExtra"))){
# Use facetting to make connection with plot 1 clearer
blob1_cl <- blob1_cl |>
  mutate(data = "A")
blob2_cl <- blob2_cl |>
  mutate(data = "B")
blob3_cl <- blob3_cl |>
  mutate(data = "C")

blob_all <- bind_rows(blob1_cl, blob2_cl, blob3_cl) |>
  pivot_longer(c(V1, V2), names_to = "var", values_to = "value")

ggplot(blob_all, aes(value, fill=cl)) + 
  geom_histogram(breaks = seq(0, 1, 0.1), 
                 colour="white", linewidth=0.2) +
  scale_fill_discrete_divergingx(palette="Zissou 1") +
  ylim(c(0,37)) +
  facet_grid(var~data) +
  theme(legend.position = "none", 
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())

# Generate a figure to show why linear combinations are needed, and subsetting
blob1_cl <- blob1_cl |>
  mutate(vars_in = ifelse(cl %in% c(1,2), "yes", "no"))
#b13 <- ggplot(filter(blob1_cl, cl %in% c(1,2)), 
#              aes(x=V1, y=1, colour=cl)) + 
b13 <- ggplot(blob1_cl, 
                aes(x=V1, y=1, colour=cl, alpha=vars_in)) + 
  geom_quasirandom() +
  #scale_colour_manual(values=c("#3B99B1", "#9FC095")) +
  scale_colour_discrete_divergingx(palette="Zissou 1") +
  scale_alpha_manual("", values=c(0.2, 1)) +
  annotate("text", x=0.05, y=1.4, label="A", size=8) +
  #xlab("linear combination") +
  ylim(c(0.5, 1.5)) +
  theme(legend.position = "none", 
        axis.text = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())

blob2_cl <- blob2_cl |>
  mutate(V1_V2 = 0.7218934*V1 - 0.6920043*V2) |>
  mutate(V1_V2 = (V1_V2 - min(V1_V2))/(max(V1_V2)-min(V1_V2))) |>
  mutate(vars_in = ifelse(cl %in% c(1,2), "yes", "no"))

#b14 <- ggplot(filter(blob2_cl, cl %in% c(1,2)), 
#              aes(x=V1_V2, y=1, colour=cl)) + 
b14 <- ggplot(blob2_cl, 
                aes(x=V1_V2, y=1, colour=cl, alpha=vars_in)) + 
  geom_quasirandom() +
  #scale_colour_manual(values=c("#3B99B1", "#9FC095")) +
  scale_colour_discrete_divergingx(palette="Zissou 1") +
  scale_alpha_manual("", values=c(0.2, 1)) +
  annotate("text", x=0.05, y=1.4, label="B", size=8) +
  xlab("linear combination") +
  ylim(c(0.5, 1.5)) +
  theme(legend.position = "none", 
        axis.text = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())

# Use PC1 for data C
prcomp(blob3_cl[,1:2])
blob3_cl <- blob3_cl |>
  mutate(V1_V2 = (0.6920043*V1 + 0.7218934*V2)/sqrt(2))

b15 <- ggplot(blob3_cl, aes(x=V1_V2, y=1, colour=cl)) + 
  geom_quasirandom() +
  scale_colour_discrete_divergingx(palette="Zissou 1") +
  annotate("text", x=0.05, y=1.4, label="C", size=8) +
  xlab("linear combination") +
  ylim(c(0.5, 1.5)) +
  theme(legend.position = "none", 
        axis.text = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())
b13 + b14 + b15 + plot_layout(ncol=3)
}
```


## Interactive interface for partitioning

Figure 4 was produced using manual graphical editing, but only aims to give an overview on the GUI anyways.

## Austrian Vacation Activities dataset

Please don't forget to set the working directory to the downloaded repo when working with /scripts/load_snapshots.R.

Figure 5 can be reproduced by running /scripts/austrian_tourism.R


```{r figure 5}
if (requireNamespace(c("gridExtra",
                       "patchwork",
                       "gridExtra"))){
# Check random projections
data(winterActiv)
set.seed(630)
t1 <- save_history(winterActiv, max=20)
t1i <- interpolate(t1)

proj1 <- matrix(t1i[,,1], nrow=27, ncol=2)
proj2 <- matrix(t1i[,,3], nrow=27, ncol=2)
proj3 <- matrix(t1i[,,15], nrow=27, ncol=2)
proj4 <- matrix(t1i[,,30], nrow=27, ncol=2)

p1 <- render_proj(winterActiv, proj1)
plot1 <- ggplot() +
  geom_point(data=p1$data_prj, aes(x=P1, y=P2)) +
  theme_bw() +
  theme(aspect.ratio=1,
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        panel.grid=element_blank()) +
  labs(x = "Alpine skiing", y = "Cross country skiing")

p2 <- render_proj(winterActiv, proj2)
plot2 <- ggplot() +
  geom_point(data=p2$data_prj, aes(x=P1, y=P2)) +
  theme_bw() +
  theme(aspect.ratio=1,
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        panel.grid=element_blank()) +
  labs(x = "Projection 1", y = "Projection 2")

p3 <- render_proj(winterActiv, proj3)
plot3 <- ggplot() +
  geom_point(data=p3$data_prj, aes(x=P1, y=P2)) +
  theme_bw() +
  theme(aspect.ratio=1,
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        panel.grid=element_blank()) +
  labs(x = "Projection 1", y = "Projection 2")

p4 <- render_proj(winterActiv, proj4)
plot4 <- ggplot() +
  geom_point(data=p4$data_prj, aes(x=P1, y=P2)) +
  theme_bw() +
  theme(aspect.ratio=1,
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        panel.grid=element_blank()) +
  labs(x = "Projection 1", y = "Projection 2")

combined_plot <- (plot1 | plot2 | plot3 | plot4) +
  plot_layout(ncol = 2, nrow = 2) + 
  plot_annotation(tag_levels = 'A') &
  theme(
    plot.tag = element_text(size = 22, face = "bold"),  # Adjust the size of the annotation tags
    axis.title.x = element_text(size = 16),  # Adjust the size of the x-axis labels
    axis.title.y = element_text(size = 16),  # Adjust the size of the y-axis labels
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(5, 5, 5, 5)
  )

combined_plot
}
```

Figures 6 and 7 can be reproduced by running /scripts/austrian_tourism_clustering.R


```{r figure 6}
if (requireNamespace(c("flexclust",
                       "stats"))){
# perform initial k-means clustering
set.seed(1234)
data(winterActiv)
clusters_full = stepcclust(winterActiv, k=6, nrep=20,  save.data=TRUE)

if (check_venv()){
init_env(env_name = "r-lionfish", virtual_env = "virtual_env")
} else if (check_conda_env()){
init_env(env_name = "r-lionfish", virtual_env = "anaconda")
}

# Figure 6 A
obj1 <- list(type = "heatmap", obj = c("Intra cluster fraction"))
if (interactive()){
interactive_tour(data=winterActiv,
                 plot_objects = list(obj1),
                 feature_names= colnames(winterActiv),
                 preselection = clusters_full@cluster,
                 n_subsets = 6,
                 display_size = 7)
}

# Figure 6 B
obj1 <- list(type = "heatmap", obj = c("Intra feature fraction"))
if (interactive()){
interactive_tour(data=winterActiv,
                 plot_objects = list(obj1),
                 feature_names= colnames(winterActiv),
                 preselection = clusters_full@cluster,
                 n_subsets = 6,
                 color_scale_heatmap = "coolwarm",
                 display_size = 7)
}
}
```

```{r figure 7}
if (requireNamespace(c("flexclust",
                        "stats"))){
# perform initial k-means clustering
set.seed(1234)
data(winterActiv)
clusters_full = stepcclust(winterActiv, k=6, nrep=20,  save.data=TRUE)

# Figure 7 A
plot(Silhouette(clusters_full))

# Figure 7 B
winterActiv_features <- c("alpine.skiing", "going.to.a.spa", "using.health.facilities",
                         "hiking", "going.for.walks","excursions",
                         "going.out.in.the.evening", "going.to.discos.bars",
                         "shopping", "sight.seeing", "museums", "pool.sauna")
winterActiv_feat_subset <- winterActiv[, colnames(winterActiv) %in% winterActiv_features]
clusters_feat_subset = stepcclust(winterActiv_feat_subset, k=6, nrep=20,  save.data=TRUE)
plot(Silhouette(clusters_feat_subset))
}
```

To launch the GUI snapshots, the data has to be prepared first.

```{r prepare winterActiv data}
# load Austrian Vacation Activities dataset
data(winterActiv)
winterActiv_features <- c("alpine.skiing", "going.to.a.spa", "using.health.facilities",
                         "hiking", "going.for.walks","excursions",
                         "going.out.in.the.evening", "going.to.discos.bars",
                         "shopping", "sight.seeing", "museums", "pool.sauna")
winterActiv_feat_subset <- winterActiv[, colnames(winterActiv) %in% winterActiv_features]
cluster_names <- paste("Cluster", 1:9)
```

Figures 8 and 9 can be reproduced by loading the contents of
/saves/aut_saves/init as shown in /scripts/load_snapshots.R. The
corresponding display is on the top left. Subplots 8 A-F can be
reproduced by highlighting the respective cluster and desaturating the
others by clicking the color boxes of the respective clusters in the
menu on the left. The blendout threshold was set to 0.1.

```{r figures 8 and 9}
if (interactive()){
load_interactive_tour(winterActiv_feat_subset, "/saves/aut_saves/init",
                      preselection_names = cluster_names[1:6],
                      hover_cutoff=20,
                      display_size = 5)
}
```

Figure 10 can be reproduced by loading the contents of
/saves/aut_saves/before as shown in /scripts/load_snapshots.R. The
blendout threshold was set to 0.1.

```{r figure 10}
if (interactive()){
load_interactive_tour(winterActiv_feat_subset, "/saves/aut_saves/before",
                      preselection_names = cluster_names[1:6],
                      hover_cutoff=20,
                      display_size = 5)
}
```

Figure 11 can be reproduced by loading the contents of
/saves/aut_saves/after as shown in /scripts/load_snapshots.R. The
blendout threshold was set to 0.1.

```{r figure 11}
if (interactive()){
load_interactive_tour(winterActiv_feat_subset, "/saves/aut_saves/after",
                      preselection_names = cluster_names[1:7],
                      hover_cutoff=20,
                      display_size = 5)
}
```

## Australian Vacation Activities dataset

To launch the GUI snapshots, the data has to be prepared first.

```{r prepare ausActiv data}
# load Australian Vacation Activities dataset
data(ausActiv)
ausActiv <- ausActiv[rowSums(ausActiv) > 0 & rowSums(ausActiv) <= 40, ]

ausActiv_features <- c("Beach","Farm","Whale","Riding",
                       "Fishing","WaterSport","Theatre","Museum",
                       "CharterBoat","Wildlife","Sightseeing",
                       "Friends","Pubs","Shopping","Casino",
                       "Relaxing", "Festivals")
ausActiv_feat_subset <- ausActiv[, colnames(ausActiv) %in% ausActiv_features]

# define cluster vector
cluster_names <- paste("Cluster", 1:9)
```

Figure 12 can be reproduced by running
/scripts/austrian_tourism_clustering.R

```{r figure 12}
if (requireNamespace("flexclust")){
data("ausActiv")
ausActiv <- ausActiv[rowSums(ausActiv) > 0 & rowSums(ausActiv) <= 40, ]
set.seed(1234)

# Figure 12
dist_matrix_f <- dist(t(ausActiv), method="binary")
ward_cluster_f <- hclust(dist_matrix_f, "ward.D2")
plot(ward_cluster_f)

clusters_f <- cutree(ward_cluster_f, k = 15)
plot(ward_cluster_f, main = "Dendrogram of Australian Vacation Activities",
     sub = "", xlab = "", ylab = "Height")
rect_info <- rect.hclust(ward_cluster_f, k = 15, border = 2:16)
}
```

Figures 13 can be reproduced by loading the contents of
/saves/aus_saves/before as shown in /scripts/load_snapshots.R.

```{r figure 13}
if (interactive()){
load_interactive_tour(ausActiv_feat_subset, "/saves/aus_saves/before",
                      preselection_names = cluster_names[1:6],
                      hover_cutoff=20,
                      display_size = 5)
}
```

Figures 14 can be reproduced by loading the contents of
/saves/aus_saves/after as shown in /scripts/load_snapshots.R.

```{r figure 14}
if (interactive()){
load_interactive_tour(ausActiv_feat_subset, "/saves/aus_saves/after",
                      preselection_names = cluster_names[1:9],
                      hover_cutoff=20,
                      display_size = 5)
}
```


## Tourist risk taking dataset

```{r load risk dataset}
data(risk)
dup <- duplicated(risk)
risk <- risk[!dup,]
```

Figure 15 can be reproduced by loading the contents of
/saves/risk_saves/final_projection_risk as shown in
/scripts/load_snapshots.R.

```{r figure 15}
if (interactive()){
load_interactive_tour(risk, "/saves/risk_saves/final_projection_risk",
                      preselection_names = cluster_names[1:5],
                      hover_cutoff=20,
                      display_size = 5.5)
}
```

Figure 16 can be reproduced by clicking the on the dropdown menu on the
bottom left, selecting "Guided tour - LDA - regroup" and then pressing
the "Run tour" button below the dropdown menu.

Figure 17 can be reproduced by loading the contents of
/saves/risk_saves/regrouped_risk as shown in /scripts/load_snapshots.R.


```{r figure 17, eval=FALSE}
if (interactive()){
load_interactive_tour(risk, "/saves/risk_saves/regrouped_risk",
                      preselection_names = cluster_names[1:5],
                      hover_cutoff=20,
                      display_size = 6)
}
```


## Launch interactive tours from scratch

```{r interactive tours from scratch,results = 'hide', warning=FALSE, message=FALSE}
if (requireNamespace(c("flexclust",
                       "stats",
                       "dplyr",
                       "data.table"))){

# set working directory to path/to/lionfish_article/
# setwd("..")
  
if (check_venv()){
init_env(env_name = "r-lionfish", virtual_env = "virtual_env")
} else if (check_conda_env()){
init_env(env_name = "r-lionfish", virtual_env = "anaconda")
}
  
######## Austrian Tourism ########

set.seed(1234)
data(winterActiv)
clusters_full = stepcclust(winterActiv, k=6, nrep=20,  save.data=TRUE)
features_to_keep <- c("alpine.skiing", "going.to.a.spa", "using.health.facilities",
                      "hiking", "going.for.walks","excursions",
                      "going.out.in.the.evening", "going.to.discos.bars",
                      "shopping", "sight.seeing", "museums", "pool.sauna")
winterActiv_feat_subset <- winterActiv[, features_to_keep]
clusters_feat_subset = stepcclust(winterActiv_feat_subset, k=6, nrep=20,  save.data=TRUE)

lda_tour_history_2d <- save_history(winterActiv_feat_subset, 
                                    tour_path = guided_tour(lda_pp(clusters_feat_subset@cluster),d=2))
lda_tour_history_1d <- save_history(winterActiv_feat_subset, 
                                    tour_path = guided_tour(lda_pp(clusters_feat_subset@cluster),d=1))

half_range <- max(sqrt(rowSums(winterActiv_feat_subset^2)))
col_names <- colnames(winterActiv_feat_subset)

obj1 <- list(type = "2d_tour", obj = lda_tour_history_2d)
obj2 <- list(type = "heatmap", obj = c("total fraction"))
obj3 <- list(type = "1d_tour", obj = lda_tour_history_1d)
obj4 <- list(type = "mosaic", obj = c("subgroups_on_y"))

if (interactive()){
interactive_tour(data=winterActiv_feat_subset,
                 plot_objects = list(obj1, obj2, obj3, obj4),
                 feature_names=col_names,
                 half_range=2,
                 n_plot_cols=2,
                 preselection = clusters_feat_subset@cluster,
                 display_size = 5)
}

######## Australian Tourism ########

data("ausActiv")

ausActiv <- ausActiv[rowSums(ausActiv) > 0 & rowSums(ausActiv) <= 40, ]
ausActiv_features <- c("Beach","Farm","Whale","Riding",
                       "Fishing","WaterSport","Theatre","Museum",
                       "CharterBoat","Wildlife","Sightseeing",
                       "Friends","Pubs","Shopping","Casino",
                       "Relaxing", "Festivals")
ausActiv_feat_subset <- ausActiv[, colnames(ausActiv) %in% ausActiv_features]

# The subset selection might deviate slightly depending on seed
# The original subset selection can be loaded form saves with

# subset_selection <- read.csv("saves/aus_saves/before/subset_selection.csv", header = TRUE)
# subsets <- subset_selection[order(subset_selection$observation_index), ]$subset

clusters <- stepcclust(ausActiv_feat_subset, k=6, nrep=20,  save.data=TRUE)
subsets <- clusters@cluster

lda_tour_history_2d <- save_history(ausActiv_feat_subset,
                                    tour_path = guided_tour(lda_pp(subsets),d=2))

lda_tour_history_1d <- save_history(ausActiv_feat_subset,
                                    tour_path = guided_tour(lda_pp(subsets),d=1))

half_range <- 2
col_names <- colnames(ausActiv_feat_subset)

obj1 <- list(type = "2d_tour", obj = lda_tour_history_2d)
obj2 <- list(type = "1d_tour", obj = lda_tour_history_1d)
obj3 <- list(type = "mosaic", obj = c("subgroups_on_y"))
obj4 <- list(type = "heatmap", obj = c("Intra cluster fraction"))

if (interactive()){
interactive_tour(data=ausActiv_feat_subset,
                 feature_names = col_names,
                 plot_objects = list(obj1, obj2, obj3, obj4),
                 half_range=half_range,
                 preselection = subsets,
                 n_plot_cols = 2,
                 n_subsets = 10,
                 display_size = 5,
                 hover_cutoff = 50)
}


######## Risk ########

data("risk")

data <- data.table(risk)
data <- apply(data, 2, function(x) (x-mean(x))/sd(x))

set.seed(1145)
r_km <- kmeans(data, centers=5,
               iter.max = 500, nstart = 5)

r_km_d <- as_tibble(data) |>
  mutate(cl = factor(r_km$cluster))
r_km_d <- as.data.table(r_km_d)

for (i in 1:7) {
  r_km_d[, paste0("cluster", i) := as.integer(cl == i)+1]
}

clusters <- r_km_d$cl

guided_tour_history <- save_history(data,
                                    tour_path = guided_tour(lda_pp(clusters)))

half_range <- max(sqrt(rowSums(data^2)))
feature_names <- colnames(data)
cluster_names <- paste("Cluster", 1:5)

# swap clusters to be more colorblind friendly
clusters <- as.numeric(as.character(clusters))
clusters_swapped <- case_when(
  clusters == 3 ~ 5,
  clusters == 5 ~ 3,
  clusters == 1 ~ 2,
  clusters == 2 ~ 1,
  TRUE ~ clusters
)

obj1 <- list(type="2d_tour", obj=guided_tour_history)

if (interactive()){
interactive_tour(data=data.matrix(data),
                 plot_objects=list(obj1),
                 feature_names=feature_names,
                 half_range=half_range,
                 n_plot_cols=2,
                 preselection=clusters_swapped,
                 preselection_names=cluster_names,
                 n_subsets=5,
                 display_size=9)
  }
}
```
