---
title: "Market segmentation"
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

This document will guide readers through how to reproduce the results
presented in the article [Interactively Visualizing Multivariate Market
Segmentation Using the R Package
Lionfish](https://github.com/mmedl94/lionfish_article) submitted to the
[Austrian Journal of Statistics](https://www.ajs.or.at/index.php/ajs).

## Installation of lionfish

You can install the development version of lionfish from github with:

```{r setup}
install.packages("remotes")
remotes::install_github("mmedl94/lionfish")
```

Make sure you have git installed. You can download and install git from
<https://git-scm.com/downloads>.

Complications may arise when installing and accessing the Python backend
of this package. If you run into any, please don't refrain from opening
an issue!

#### Complications for windows users 

Running the example code below might result in the following error

Error: Required version of NumPy not available: incompatible NumPy
binary version 33554432 (expecting version 16777225) To resolve this, we
have to delete the erroneous virtual environment and build a new one
with an older Python version.

```{r setup}
# Delete the old enironment, might require a restart of R
reticulate::virtualenv_remove("r-lionfish")

# Install the stable Python version
reticulate::install_python(version="3.8.10")

# Build new virtual environment
reticulate::virtualenv_create(envname = "r-lionfish", version="3.8.10")

# Initiate Python environment as usual
init_env()
```
